% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\usepackage{fullpage}
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
%\setlength{\headheight}{24pt} % allow room for 2-line header
%\setlength{\headsep}{24pt}  % space between header and text
%\setlength{\headheight}{24pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
\cfoot{}                                     % the foot is empty
%\topmargin=-0.5in % start text higher on the page

\newcommand{\reducevspace}{\vspace{-4pt}}

\begin{document}
\thispagestyle{empty} % this page has no header  
\name{JESSE THOMASON\\[12pt]}% the \\[12pt] adds a blank line after name

\address{jessethomason.com \\
jesse@cs.utexas.edu \\ (501) 282-3663}     

\address{916 E 39th Street \\ Unit B \\ Austin, TX 78751}

\begin{resume}

\section{\centerline{ SKILLS and INTERESTS }}

{\sl Languages:} strong in \textbf{Python}, \textbf{C++}; experince with Java, PHP, and Javascript \\
{\sl Research Areas:} \textbf{Natural Language Processing} (Language Grounding, Semantic Parsing); \\
\hspace*{75.5pt} Human-Robot/Human-Computer Interaction; and Machine Learning

\section{\centerline{EDUCATION}} 

{\sl University of Texas at Austin}, PhD Computer Science (in progress) \hfill 2013-Present
  \begin{itemize} \itemsep -2pt
  \item Graduate Student of Dr. Raymond J. Mooney \hfill GPA 3.876
  \item Planning to graduate in May 2018
  \item Select Coursework: Natural Language Processing, Semantics I, Machine Learning
  \item Awards: \textbf{National Science Foundation Graduate Research Fellowship} (2015) \\
  \hspace*{36.5pt} UTCS Microelectronics and Computer Development Fellowship (2013)
 \end{itemize}
\reducevspace
{\sl University of Pittsburgh}, BS Computer Science; Mathematics \hfill 2009-2013
  \begin{itemize} \itemsep -2pt
  \item Research Assistant for Dr. Diane Litman \hfill GPA 3.877
  \item Awards: Computer Science Outstanding Undergraduate Student Award (2013) \\
  \hspace*{37pt} Honors College Chancellor's Scholarship (2009)
 \end{itemize}

\section{\centerline{EXPERIENCE and SELECTED PUBLICATIONS}} 

{\sl Language and Robotics} \hfill University of Texas at Austin

  \begin{itemize} \itemsep -2pt % reduce space between items
  \item Performed \textbf{grounded language learning} in multi-modality sensory contexts on an embodied robot through \textbf{human-robot interaction} games.
  \item \textit{Opportunistic Active Learning for Grounding Natural Language Descriptions.} \\
  Proceedings of the 1st Annual Conference on Robot Learning (\textbf{CoRL-17}).\footnote{https://scholar.google.com/citations?user=8BeTDr0AAAAJ}
  \item \textit{Learning Multi-Modal Grounded Linguistic Semantics by Playing ``I Spy.''} \\
  Proceedings of the 25th International Joint Conference on Artificial Intelligence (\textbf{IJCAI-16}).
  \item Explored \textbf{dialog-assisted semantic parsing} improvement on a robotic platform.
  \item \textit{Learning to Interpret Natural Language Commands through Human-Robot Dialog}. \\
  Proceedings of the 24th International Joint Conference on Artificial Intelligence (\textbf{IJCAI-15}).
 \end{itemize}
\reducevspace
{\sl Language and Vision} \hfill University of Texas at Austin

  \begin{itemize} \itemsep -2pt
  \item Combined textual and visual context to discover \textbf{polysemy and synonymy} in noun phrases.
  \item \textit{Multi-Modal Word Synset Induction.} \\
  Proceedings of the 26th International Joint Conference on Artificial Intelligence (\textbf{IJCAI-17}).
  \item Integrated vision confidence with language corpus data to improve video description.
  \item \textit{Integrating Language and Vision to Generate Natural Language Descriptions of Videos in the Wild}. \\ 
  Proceedings of the 25th International Conference on Computational Linguistics (\textbf{COLING-14}).
\end{itemize}
%\reducevspace
%{\sl Language and Human-Computer Interaction} \hfill University of Pittsburgh
%
%  \begin{itemize} \itemsep -2pt
%  \item Increased the accuracy of multiple-affect detection in a spoken dialog tutoring system
%  \item Discovered speech differences between users in Wizard-of-Oz versus fully automated experiments
%  \item \textit{Differences in User Responses to a Wizard-of-Oz versus Automated System}. \\
%  Proceedings of the 2013 Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies (\textbf{NAACL-HLT 2013}).
%  \item Studied the correlations of student entrainment to tutoring system's voice and student performance
%  \item \textit{Prosodic Entrainment and Tutoring Dialogue Success}. \\
%  Proceedings 16th International Conference on Artificial Intelligence in Education (AIED 2013).
% \end{itemize}
\reducevspace
{\sl Software Engineering Internship} \hfill Google (2016)

  \begin{itemize} \itemsep -2pt
  \item Worked on attaching semantic roles to chunked query constituents.
  \item Proposed and demonstrated a factor graph method that incorporated pre-processing and frame-based knowledge to label chunks with roles.
 \end{itemize}
%\reducevspace
%{\sl Professional} \hfill Einhorn Media Group (2011-2013)
%
%  \begin{itemize} \itemsep -2pt
%  \item Maintained and updated multiple commercial software packages distributed by the company.
%  \item Assisted in the devlopment of new software and web tools both for distribution and for local use.
% \end{itemize}
 
\end{resume} 
\end{document}